% Created 2023-06-16 Fri 13:19
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setkomavar{fromname}{Max Frey}
\setkomavar{fromemail}{maxfrey@Maxs-Mac-mini.local}
\KOMAoption{fromemail}{false}
\KOMAoption{fromphone}{false}
\KOMAoption{fromurl}{false}
\KOMAoption{fromlogo}{false}
\KOMAoption{backaddress}{false}
\setkomavar{place}{}
\KOMAoptions{foldmarks=true}
\LoadLetterOption{NF}
\date{\today}
\hypersetup{
 pdfauthor={Max Frey},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.6)}, 
 pdflang={English}}
\begin{document}

\begin{letter}{%
\mbox{}}

\opening{Magit Tips}

\#+BEING\textsubscript{EXPORT} html
---
layout: default
title: Magit Tips
---
\#+END\textsubscript{EXPORT}
An extremely annoying error while learning magit branch workflows is the following:
Not a valid starting-point: <my\textsubscript{branch}>

Where does this come from, and how do we resolve it? 

Recall that to check out a branch from magit, after navigating to the magit-status page, we press b n

Then, magit will ask you for your starting place. This is actually very helpful - we frequently want to create a branch not from master, but from some other existing branch. But here in lies the issue. It's asking for the starting place. 

Be careful: magit is NOT asking you to name your new branch yet. If you choose a branch that does not exist, you will see the following:

Not a valid starting-point: my-new-branch

\ldots{} so -- choose a branch that exists! THEN magit will ask you to create your branch.
\closing{}




\end{letter}

\end{document}